---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(BDEEPInfousa)
```

get_infousa_location

This function gets a data.frame including all data from the given location in a single year.

Parameter:
    
    single_year   An integer indicating a single year
    
    loc           A vector of integers indicating fips ("fips" method) or a data.frame with first 2 columns being state abbr. & county name ("names" method).If the entire state is needed, set county code to 000 ("fips") or set county name to "*" ("names").
    
    tract         A vector of integers or chars indicating tract in the county. Note that tracts are unique only in the current county. Default to all tracts.
    
    columns       A vector of column names to export. Default to all columns (i.e. "*").
    
    method        Method for input. Choose between "fips" and "names". Default to "fips".
    
    append        If append is true, return a single data.frame with rows appended, otherwise a
                     list of data.frames from each state.

```{r}
data <- get_infousa_location(2006, "01001")
head(data, n = 5L)
test <- get_infousa_location(2006, "02020", tract=c(001802,002900))
head(data, n = 5L)

x <- data.frame(state=c('il'), county=c('champaign'))
data <- get_infousa_location(2017, x, method="names")
head(data, n = 5L)
```


get_infousa_multiyear

This function gets a data.frame including all data from the given location from all years.

Parameter:

    startyear     The first year to get data
    
    endyear       The last year to get data
    loc           A vector of integers indicating fips ("fips" method) or a data.frame with first 2 columns being state abbr. & county name ("names" method).If the entire state is needed, set county code to 000 ("fips") or set county name to "*" ("names").
    
    tract         A vector of integers or chars indicating tract in the county. Note that tracts are unique only in the current county. Default to all tracts.

    columns       A vector of column names to export. Default to all columns (i.e. "*").

    method        Method for input. Choose between "fips" and "names". Default to "fips".
    
```{r}
data <- get_infousa_multiyear(2017, 2017, "01001")
head(data, n = 5L)
data <- get_infousa_multiyear(2006, 2016, "02020", tract=c(001802,002900))
head(data, n = 5L)
```

get_infousa_zip

This function gets a data.frame including all data from the given location from all years.

Parameter:

    startyear     The first year to get data

    endyear       The last year to get data

    zip           A vector of characters indicating zipcodes to get data from.

    columns       A vector of column names to export. Default to all columns (i.e. "*").

```{r}
data <- get_infousa_zip(2016, 2017, c("61801", "61820"))
head(data, n = 5L)
```

get_infousa_fid

This function gets a data.frame including all data from the given vector of familyid from given years.

Parameter:

    startyear     The first year to get data
    
    endyear       The last year to get data
    
    fid           A vector of characters indicating familyids to get data from.
    
    columns       A vector of column names to export. Default to all columns (i.e. "*").
    
```{r}
data <- get_infousa_fid(2006, 2007, c("54299524", "54320129"))
head(data, n = 5L)
```

get_infousa_usr 

This function gets from database according to a user-specified query.

Parameter:

    query         A string specifying the query sent to database
    
    database_name A string indicating the database name
    
    host_ip       A string indicating the ip address of the database VM
    
```{r}
# Select single field from a given table
data <- get_infousa_usr("SELECT year2006part.total limit 50")
head(data, n = 5L)
```

